\textbf{Proof Reconstruction in Classical Propositional Logic}

### 2017-04-27 slides/slides.tex
[ slides ] alejandro no deja trabajar.

\begin{frame}[fragile, label=atp-conjunct]{Conjunct}{Inference Rule}

@@

\item Function:
\begin{agda}
conjunct : Prop → Prop → Prop
conjunct $(φ \wedge ψ)$ $ω$ with $⌊$ eq $φ$ $ω$ $⌋$ | $⌊$ eq ψ $ω$ $⌋$
... | true  | _     = $φ$
... | false | true  = $ψ$
... | false | false = conjunct $φ$ $ω$
conjunct $φ$ $ω$       = $φ$
\end{agda}
\item Theorem
\begin{agda}
atp-conjunct
  : ∀ $\{Γ\}$ $\{φ\}$
  → $(ω : Prop)$
  → $Γ \vdash φ$
  → $Γ \vdash$ conjunct $φ$ $ω$
\end{agda}
\end{itemize}
\end{frame}

\begin{frame}[fragile, label=agda-file]{Agda Code Example}{Generated by Athena Tool}
\begin{tikzpicture}[overlay, remember picture]
 \tikzset{shift={(current page.north)}, xshift=5cm,yshift=-2cm}
\node[vertex, fill=black] (d1) {};
\node[vertex, fill=black, right=0.5cm of d1 ] (d2) {};
\node[vertex, fill=black, below=0.2cm of d1] (d3) {};
\node[vertex, fill=black, below=0.2cm of d2] (d4) {};
\node[vertex, fill=black, below right= 0.2cm and  0.25cm of d3] (d5) {};
\draw[-, thick] (d1) to (d3);
\draw[-, thick] (d2) to (d4);
\draw[-, thick] (d3) to (d5);
\draw[-, thick] (d4) to (d5);
\end{tikzpicture}

\begin{itemize}
  \item The problem is $p ∧ q ⊢ q ∧ p$
  \item TSTP derivation
\begin{tptp}
fof(a, axiom, p & q).
fof(goal, conjecture, q & p).
\end{tptp}
  \item A natural deduction proof
  \begin{prooftree}
  \AxiomC{$ϕ ∧ ψ$}
  \RightLabel{$∧$-\texttt{proj}$₁$}
  \UnaryInfC{$ϕ$}

  \AxiomC{$ϕ ∧ ψ$}
  \RightLabel{$∧$-\texttt{proj}$₂$}
  \UnaryInfC{$ψ$}
  \RightLabel{$∧$-\texttt{intro}}
  \BinaryInfC{$ψ ∧ ϕ$}
  \end{prooftree}
\end{itemize}
\gobackreconstruction
\end{frame}

\begin{frame}[fragile, label=verified-example]{Type-checked Proof}
\begin{agda}
proof$₀$ : $Γ ⊢$ subgoal$₀$
proof$₀$ =
  (RAA
    (atp-canonicalize
      (atp-simplify
        (atp-canonicalize
          (atp-strip
            (assume $\{Γ = Γ\}$
              (atp-negate subgoal$₀$))))
        (atp-conjunct (q)
          (atp-canonicalize
            (weaken (atp-negate subgoal$₀$)
              (assume $\{Γ = ∅\}$ a)))))))
\end{agda}
\gobackreconstruction
\end{frame}

\begin{frame}[fragile, label=verified-example-2]{Type-checked Proof}
\begin{agda}
proof$₁$ : $Γ ⊢$ subgoal$₁$
proof$₁$ =
  (RAA
    (atp-canonicalize
      (atp-simplify
        (atp-conjunct (q)
          (atp-canonicalize
            (weaken (atp-negate subgoal$₁$)
              (assume $\{Γ = ∅\}$ a))))
        (atp-simplify
          (atp-canonicalize
            (atp-strip
              (assume $\{Γ = Γ\}$
                (atp-negate subgoal$₁$))))
          (atp-conjunct (p)
            (atp-canonicalize
              (weaken (atp-negate subgoal$₁$)
                (assume $\{Γ = ∅\}$ a))))))))
\end{agda}
\gobackreconstruction
\end{frame}

>>>>

\begin{frame}[fragile, label=atp-conjunct]{Conjunct}{Metis Inference Rule}

@@

\item Function\footnote{\label{note-conjunct}It is available in \texttt{agda-metis} library in \texttt{ATP.Metis.Rules.Conjunct} module.}:
\begin{agda}
conjunct : Prop → Prop → Prop
conjunct $(φ \wedge ψ)$ $ω$ with $⌊$ eq $φ$ $ω$ $⌋$ | $⌊$ eq ψ $ω$ $⌋$
... | true  | _     = $φ$
... | false | true  = $ψ$
... | false | false = conjunct $φ$ $ω$
conjunct $φ$ $ω$       = $φ$
\end{agda}
\item Theorem\textsuperscript{\ref{note-conjunct}}
\begin{agda}
atp-conjunct
  : ∀ $\{Γ\}$ $\{φ\}$
  → $(ω : Prop)$
  → $Γ \vdash φ$
  → $Γ \vdash$ conjunct $φ$ $ω$
\end{agda}
\end{itemize}
\end{frame}

\begin{frame}[fragile, label=agda-file]{Agda Code Example}{Generated by Athena Tool}

\begin{itemize}
  \item The problem is $p ∧ q ⊢ q ∧ p$
  \item TPTP derivation
\begin{tptp}
fof(a, axiom, p & q).
fof(goal, conjecture, q & p).
\end{tptp}
  \item A natural deduction proof
\begin{columns}
\begin{column}{0.8\textwidth}
 \begin{prooftree}
  \AxiomC{$ϕ ∧ ψ$}
  \RightLabel{$∧$-\texttt{proj}$₁$}
  \UnaryInfC{$ϕ$}

  \AxiomC{$ϕ ∧ ψ$}
  \RightLabel{$∧$-\texttt{proj}$₂$}
  \UnaryInfC{$ψ$}
  \RightLabel{$∧$-\texttt{intro}}
  \BinaryInfC{$ψ ∧ ϕ$}
  \end{prooftree}
\end{column}
\begin{column}{0.2\textwidth}  %%<--- here
   \begin{tikzpicture}[overlay, remember picture]
% \tikzset{shift={(current page.north)}, xshift=cm,yshift=-2cm}
\node[vertex, fill=black] (d1) {};
\node[vertex, fill=black, right=0.5cm of d1 ] (d2) {};
\node[vertex, fill=black, below=0.2cm of d1] (d3) {};
\node[vertex, fill=black, below=0.2cm of d2] (d4) {};
\node[vertex, fill=black, below right= 0.2cm and  0.25cm of d3] (d5) {};
\draw[-, thick] (d1) to (d3);
\draw[-, thick] (d2) to (d4);
\draw[-, thick] (d3) to (d5);
\draw[-, thick] (d4) to (d5);
\end{tikzpicture}
\end{column}
\end{columns}

\end{itemize}
\gobackreconstruction
\end{frame}

% \begin{frame}[fragile, label=verified-example1]{TPTP}

% \end{frame}

\begin{frame}[fragile, label=verified-example]{Type-checked Proof}
\vfill
\begin{agda}
proof$₀$ : $Γ ⊢$ subgoal$₀$
proof$₀$ =
  (RAA
    (atp-canonicalize
      (atp-simplify
        (atp-canonicalize
          (atp-strip
            (assume $\{Γ = Γ\}$
              (atp-negate subgoal$₀$))))
        (atp-conjunct (q)
          (atp-canonicalize
            (weaken (atp-negate subgoal$₀$)
              (assume $\{Γ = ∅\}$ a)))))))
\end{agda}
\vfill
\gobackreconstruction
\end{frame}

\begin{frame}[fragile, label=verified-example-2]{Type-checked Proof}
\vfill
\begin{agda}
proof$₁$ : $Γ ⊢$ subgoal$₁$
proof$₁$ =
  (RAA
    (atp-canonicalize
      (atp-simplify
        (atp-conjunct (q)
          (atp-canonicalize
            (weaken (atp-negate subgoal$₁$)
              (assume $\{Γ = ∅\}$ a))))
        (atp-simplify
          (atp-canonicalize
            (atp-strip
              (assume $\{Γ = Γ\}$
                (atp-negate subgoal$₁$))))
          (atp-conjunct (p)
            (atp-canonicalize
              (weaken (atp-negate subgoal$₁$)
                (assume $\{Γ = ∅\}$ a))))))))
\end{agda}
\vfill
\gobackreconstruction
\end{frame}
